Discussion Draft

### 2020-04-10 doc/Discussion.rmd
nots while reading morelli cohen

Our results of greater between cell variation in females are supported by empiracal results from human and mouse [@lynn2002, @gruhn2013]. <More details on the empirarcal pattern>

@@

>>>>

Our results of greater between cell variation in females are supported by empiracal results from human and mouse [@lynn2002, @gruhn2013]. <More details on the empirarcal pattern> (cite morelli cohen)

@@

It also could be that the -- greater error in regulation of crossovers may have driven the longer female axis -- to esure / increase the probabilty of succesful maturation of DSB into crossover / chiasmata (cite morelli cohen)

longer female axis has evol
